Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan

### 2020-08-14 analysis/paper/paper.Rmd
update discussion section and add references

The shape variation reported here is subtle, and invites consideration of another possible scenario that the absence of major changes in vessel shape at Kiwulan may have been an act of resistance to foreign influence. We recognize the decline in population may lead to a standardized shape, however, the evidence of ceramic spatial distribution shows a dispersed or random pattern across the whole area throughout three phases. This indicates manufacturing activities may be limited to household scale and reflect a common practice in the community. The standardization in vessel shape over time draws our attention to the endurance of traditional pottery production practices amid intrusions from Europeans and Chinese. In a culture contact situation, social identity may be expressed through material practices as a means of expressing cultural homogeneity and distinction from other groups [@Voss2005].

>>>>

The shape variation reported here is subtle and invites consideration of another possible scenario that the absence of major changes in vessel shape at Kiwulan may have been an act to show ethnic identity when experiencing foreign influences [cf. @Torrence2000]. We should note that the morphology of ceramics could be treated as a signal for message communication between potters that repeating the same shape or modifying may have occurred in a non-deterministic way [@Kubler1962]. However, as the only type of locally made pottery throughout 600 years, the homogeneous and even more standardized shape in the Chinese period might convey some meaningful information. We recognize the decline in population may lead to a standardized shape, however, the evidence of ceramic spatial distribution shows a dispersed or random pattern across the whole area throughout three phases. This indicates manufacturing activities may be limited to household scale and reflect a common practice in the community. The standardization in vessel shape over time draws our attention to the endurance of traditional pottery production practices amid intrusions from Europeans and Chinese. In a culture contact situation, social identity may be expressed through material practices as a means of expressing cultural homogeneity and distinction from other groups [@Voss2005].
